---
title: "Overview of simPRS Package"
date: "`r Sys.Date()`"
output:
    html_document:
        theme: readable
        toc: true # table of content true
vignette: >
    %\VignetteIndexEntry{Overview of simPRS package}
    %\VignetteEngine{knitr::rmarkdown}
---

```{r loadKnitr, echo=FALSE, warning=FALSE}
library("knitr")
# opts_chunk$set(eval=FALSE)
# library(pander)
# panderOptions("digits", 3)
set.seed(18090212)
library(simPRS)
```

# Overview

Simulation of Polygenic Risk Score calculations allows to

1.  Select an optimal p-value threshold,
2.  Perform power analyses, and
3.  Estimate polygenicity of a phenotype.

Simulations are performed without direct simulations of the 
genotype and phenotype data. 
Instead, genome-wide association study (GWAS) summary statistics
are generated directly from their finite sample distributions.

# Sample code

## Perform a single simulation

```{r singleSimulation}
# Parameters
NTotalSNPs = 10000
NSignalSnps = 100
heritability = 0.2
signalDistr = "Same"
Ntrain = 10000
Ntest = 3000

signal = genSignal(
            NSignalSnps = NSignalSnps,
            NTotalSNPs = NTotalSNPs,
            heritability = heritability,
            signalDistr = signalDistr)
            
gwas = gwasFast(signal = signal, N = Ntrain)

prs = prsInf(
            gwasPV = gwas$pv,
            gwasBt = gwas$beta,
            signal = signal)

rci = rConfInt(r = prs$r, N = Ntest)

prsPlot(pv = prs$pv, r = prs$r, rci)
```

## Average over 1000 simulations

Let's use the parameters and `signal` defined above

```{r manySimulation}
Nsim = 1000

prsA = prsMultitest(signal = signal, N = Ntrain, Nsim = Nsim, nthreads = 2)

rci = rConfInt(r = prsA$r, N = Ntest)

prsPlot(pv = prsA$pv, r = prsA$r, rci)
```
